
\charm{Pearlescent Filigree Defense}
{1m}
{Reflexive}{One scene}{-}
{Dreaming Pearl 2}
This charm may be activated at any time. Clothing the martial artist wears hardens and strengthens, counting as mortal light armor which is compatible with this style (but not other styles which forbid armor). In addition, when targeted with a Withering attack, she may spend up to (Appearance) motes, increasing her armor's soak against that attack by that much.

\textbf{Mastery}: She gains Hardness 10 against the next Decisive attack which targets her. Gain this benefit only once per scene, even if she ends the charm and reactivates it.

\charm{Dreaming Pearl Courtesan Form}
{8m}
{Simple}{One Scene}{Form}
{Essence 2, Dreaming Pearl 4, Pearlescent Filigree Defense}
The martial artist may make Dreaming Pearl attacks out to Short range, slashing a fan to create a razor wind, a stash growing long enough to wrap ankles, throwing spikes of energy from her fingertips or similar. Any weapon enhanced by Elegant Weapon Repertoire gains the traits of a light artifact weapon, and any clothing enhanced by Pearlescent Filigree Defense gains the traits of light artifact armor.

Whenever the martial artist successfully disengages with 5+ successes, she may activate this charm reflexively.

\charm{Seven Storms Escape Prana}
{4m, 2i}
{Supplemental}{Instant}{-}
{Essence 2, Dreaming Pearl 4, Dreaming Pearl Courtesan Form}
This charm supplements a Disengage attempt, a roll made to defend against a Rush or a control roll made to defend against a grapple. The martial artist's opponent suffers a -(martial artist's Appearance) penalty. If he wins the roll and her successes exceed his Resolve, he must pay 1wp or lose the opposed roll anyway.

\textbf{Mastery}: The duration of this charm is "one round", affecting all opposed actions it could be applied to.

\charm{Vindictive Concubine's Pillow Book}
{4m}
{Supplemental}{Instant}{Post-Roll}
{Essence 3, Dreaming Pearl 5, Seven Storms Escape Prana}
This charm supplements a Decisive Dreaming Pearl attack after it's hit, increasing the damage by two per per condition met.

\begin{itemize}
  \item The martial artist is making an Ambush attack against a target who knows her personally.
  \item She knows something about his personal life or dealings that would be embarassing or ruinous to him, and he knows that she knows it.
  \item She stole Initiative from him last round with Fragrant Petal Fascination Kata this or last round.
  \item She succeeded on an action or defense using Seven Storms Escape Prana this or last round.
\end{itemize}

\textbf{Terrestrial}: This charm may only be used Once/Scene.

\textbf{Mastery}: Being in Dreaming Pearl Courtesan Form counts as an additional criteria.

\charm{Fragrant Petal Fascination Kata}
{4m}
{Supplemental}{Instant}{Group, Once/Scene}
{Essence 2, Dreaming Pearl 4, Dreaming Pearl Courtesan Form}
This charm supplements an Inspire action to fill enemies with love, lust, mercy, distraction or similar, granting it (Essence) automatic successes. In combat, she steals 1i from each enemy whose resolve is overcome, whether or not he spends willpower to resist.

\charm{Invoking the Chimera's Coils}
{8m, 1wp}
{Reflexive}{One Scene}{-}
{Essence 3, Dreaming Pearl 5, Fragrant Petal Fascination Kata}
The martial artist may activate this charm at the start of her turn when she is in Dreaming Pearl Courtesan Form and either she has Initiative 15+ or no undamaged -2 health levels. Her neck lengthens as she grows to five times her normal height, while her head becomes that of a delicate, gold-beaked foal with four sets of spiraling horns. Her arms and legs vanish, replaced with opalescent fins like those of a carp hold her new form aloft in the air. Countless eyes run down either side of her narrow snout and continue down her back, ranging from the size of small pearls to that of goose eggs, blazing like sapphires in the noonday sun.

She flies effortlessly, and her natural soak increases by (Essence). She may not make attacks with abilities other than Dreaming Pearl (including attacks created by Reflexive charms). Other Dreaming Pearl Courtesan charms are enhanced:

\begin{itemize}
  \item Pearlescent Filigree Defense: The enhanced clothing gains an additional +3 soak and hardness.
  \item Fragrant Petal Fascination Kata: She steals an additional 2i from each opponent whose Resolve is overcome.
  \item Seven Storms Escape Prana: This charm may now supplement any movement action (including those unopposed), allowing her to ignore intervening barriers and hazards as she dissolves into pastel fumes and reappears at her destination in a vortex of swirling light.
  \item Vindictive Concubine's Pillow Book: The damage increases by a further 2.
\end{itemize}

If she suffers any damage to a -4 health level, she becomes so caught up in her dream that she vanishes from the world entirely, never to be seen again.

\textbf{Terrestrial}: If she ends her turn below 10 Initiative and didn't hit with a Decisive attack or gambit on her turn, the charm ends.

\textbf{Mastery}: When activating this charm for the first time in a scene, she rolls Join Battle using (Appearance + Performance), adding to her existing initiative total.

\charm{Invoking the Chimera's Coils (Alternate Version)}
{8m, 1wp}
{Simple}{One Scene}{Perilous}
{Essence 3, Dreaming Pearl 5, Seven Storms Escape Prana, Vindictive Concubine's Pillow Book}
The martial artist may activate this charm while at 10+ Initiative and in Dreaming Pearl Courtesan Form, and ends if she leaves the form. She becomes dreamlike and luminous, seeming to fade in and out of reality like a half-remembered dream. Her other Dreaming Pearl charms are enhanced:

\begin{itemize}
  \item Pearlescent Filigree Defense: The enhanced clothing gains an additional +3 soak and hardness.
  \item Fragrant Petal Fascination Kata: She steals an additional 1i from each opponent whose Resolve is overcome.
  \item Seven Storms Escape Prana: Reduce the cost of this charm by 2m. She may spend initiative she doesn't have on it, taking her into the negative (or further into it).
  \item Vindictive Concubine's Pillow Book: The damage increases by another 2.
\end{itemize}

\textbf{Terrestrial}: If she ends her turn below 10 Initiative and didn't hit with a Decisive attack or gambit on her turn, the charm ends.

\textbf{Mastery}: This charm loses the Perilous keyword.
