
\charm{Snake Form}
{8m}
{Simple}{One Scene}{Form}
{Snake 4, Essence 1}
The martial artist adds (Dexterity) to her soak. Enemies suffer a -1 penalty on attack rolls against the martial artist, or -3 if she has Advantage over them. She may activate this charm reflexively whenever she makes a withering attack that grants her Advantage over an opponent (where she didn't previously have it).

With an Essence 2+ repurchase, she may spend an additional 1wp when activating this charm to gain an additional +(Essence) soak, and increase the raw damage of all Withering attacks she makes by +2.

\textbf{Mastery}: The repurchase's damage bonus also applies to Decisive attacks against enemies she has Advantage over.

\charm{Armor-Penetrating Fang Strike}
{5m, 1wp}
{Supplemental}{Instant}{-}
{Essence 2, Snake 5, Snake Form}
This charm supplements any Snake attack, allowing the martial artist to ignore the enemy's soak or hardness.

\textbf{Terrestrial}: This charm gains the Once/Scene keyword, and can be reset by dealing 3+ levels of damage with a decisive Snake attack and raising her initiative back up to 12+.

\charm{Snake Strikes the Heel}
{2m, 1wp}
{Reflexive}{Instant}{-}
{Essence 2, Snake 4, Snake Form}
This charm may be activated any time Solar is targeted by an attack from Close range (or further, if she knows and uses Uncoiling Serpent Prana). She clashes the attack with a Snake attack of her own. If she clashes with a withering attack, she does not gain any initiative even if she succeeds; if she clashes with a decisive attack, she must attempt a gambit rather than dealing damage.

\textbf{Terrestrial}: This charm gains the Attack-Action keyword.

\charm{Crippling Pressure-Point Strike}
{3m, 3+i}
{Supplemental}{Instant}{-}
{Essence 2, Snake 4, Snake Form}
This charm supplements a decisive Snake attack with one of the following benefits:

\begin{itemize}
  \item Blinding Fang Strike (3i): If she hits, her enemy suffers a -3 penalty on all actions and is blinded for the rest of the scene. He may spend an unflurable miscellaneous action to remove these penalties.
  \item Nerve-Deadening Venom (4i): If she hits, one of the victims arms is paralized for the rest of the scene, and he suffers a -2 penalty on all actions that would normally require the use of both hands.
  \item Withering Venom Paralysis (6i): If she hits, her enemy's lower body is paralzied until the end of the scene, knocking him prone. Even if he succeeds on a Rise from Prone action he can only crawl, treating all terrain as difficult and taking a -3 penalty on movement actions.
\end{itemize}

\textbf{Terrestrial}: The marital artist cannot use Withering Venom Paralysis.

\charm{Uncoiling Serpent Prana}
{7m, 3i}
{Supplemental}{Instant}{Advantage}
{Essence 3, Snake 4, Snake Strikes the Heel, Armor-Penetrating Fang Strike}
This charm supplements any Snake attack while the martial artist is in Snake Form, allowing her to strike at up to Medium range using a serpentine ribbon of essence. If the attack deals 5+ Initiative damage or any decisive damage, she may drag her enemy into Close range.

\textbf{Terrestrial}: The martial artist may only make this attack at Short range rather than medium.

\textbf{Mastery}: The martial artist does not need to be in Snake Form to use this charm.

\charm{Countless Coils Evasion}
{7m, 1wp}
{Supplemental}{Instant}{Perilous, Post-Roll}
{Essence 3, Snake 5, Snake Strikes the Heel, Crippling Pressure-Point Strike}
This charm supplements the martial artist's defense against a decisive attack, after it rolls damage. She rolls (Essence + Initiative), and each success negates one level of damage from the attack. She resets to base initiative, and if she negated all the damage, gains 2i.

\textbf{Terrestrial}: The martial artist must decide to use this charm before damage is rolled (but still rolls and applies the effects after damage).
