
\charm{Tiger Form}
{10m}
{Simple}{One scene}{Form}
{Tiger 4, Essence 1}
The martial artist doubles up to (Strength) threshold successes for purposes of calculating the raw damage of withering attacks, and takes no penalty for fighting while prone. She adds (Essence) dice to Rush actions and rolls to contest Disengage attempts. She gains the initiative her enemies spend attempting to disengage from her.

She may activate this charm reflexively whenever she lands any decisive attack that deals 3+ levels of damage.

\textbf{Terrestrial}: The martial artist only doubles up to the lowest of Strength, Dexterity, and Wits threshold successes when calculating withering damage.

\charm{Stalking Cat Movement}
{5m}
{Reflexive}{One Scene}{-}
{Essence 2, Tiger 4, Tiger Form}
Enemies at short or medium range must use Disengage actions to move away from the martial artist as though she were at close range to them. They take -1 penalty on their defense against surprise attacks she makes.

\textbf{Mastery}: The martial artist may Rush enemies while in stealth.

\charm{Raging Tiger Pounce}
{4m}
{Supplemental}{Instant}{-}
{Essence 2, Tiger 4, Tiger Form}
This charm supplements any Tiger attack. If it deals at least one level of damage, the martial artist's enemy is knocked prone. As long as he remains within Close range of her, she steals 2i whenever he attempts to Rise from Prone.

\textbf{Mastery}: This charm can also supplement an attack against a prone enemy, rendering it undodgeable and adding +1 raw damage.

\charm{Celestial Tiger Hide}
{5m}
{Reflexive}{One scene}{Once/Scene}
{Essence 2, Tiger 5, Stalking Cat Movement}
This charm may be activated at any time. The martial artist adds (Strength) to her natural soak and gains (Essence) hardness. She increases both values by +2 against attacks made from long or extreme range.

When struck by a decisive attack, she may spend 1wp and end this charm to reduce its raw damage by her Hardness.

\textbf{Terrestrial}: The martial artist must spend 2wp instead of 1wp to end the charm when struck by a decisive attack.

\charm{Spine-Shattering Bite}
{5m, 1wp}
{Supplemental}{Instant}{Post-roll}
{Essence 3, Tiger 5, Raging Tiger Pounce}
This charm supplements a decisive Tiger attack after the martial artist rolls at least three levels of damage. She reduces the damage by two levels and cripples him instead. He may not take movement actions until he shakes off the paralysis, a miscellaneous action costing 2i and requiring a (Stamina + Resistance) roll, difficulty (Martial Artist's Strength).

\textbf{Terrestrial}: This charm gains the Once/Scene Keyword

\charm{Angry Predator Frenzy}
{5m, 1wp}
{Reflexive}{One Scene}{-}
{Essence 3, Tiger 5, Celestial Tiger Hide, Spine-Shattering Bite}
This charm may be activated at any time while the martial artist is in Tiger Form, and it ends if she leaves the form. On decisive attacks she adds up to (Strength) threshold successes to the raw damage, and can Rush once per round as a reflexive action, in addition to her normal movement, but cannot Disengage or Withdraw. She gains a Defining Tie of savage hatred against her foes while this charm lasts

\textbf{Terrestrial}: The martial artist adds only (lower of Strength or Essence) to the damage of decisive attacks.

\textbf{Mastery}: The martial artist's base initiative increases by (Strength / 2, rounded up).
